### 2021-11-05 manuscript.Rmd
Figure 6: Added legend for corrected ES estimate

|  | Group-Sequential Design | Independent Segments Procedure | Sequential Bayes Factor Design |
| ------------- | ------------- | ------------- | ------------- |
| **Aim** | Efficiently reject $H_0$ in favor of an alternative $H_1$ | Efficiently reject $H_0$ in favor of an alternative $H_1$ | Efficiently examine the evidence for $H_0$ relative to an alternative $H_1$, or vice versa |
| **Nature of data**  | Cumulative  | Independent  | Cumulative  | Cumulative |
| **Control of error rates** | Direct | Direct | Indirect (e.g., through simulation) |
| **Bias correction procedure**| Available | Does not exist | Available |
| **Flexibility** | Moderately flexible | Highly restrictive | Highly flexible |
| **Acceptance of the null** | Possible | Impossible | Possible |

>>>>

|  | Group-Sequential Designs | Independent Segments Procedure | Sequential Bayes Factor Design |
| ------------- | ------------- | ------------- | ------------- |
| **Aim** | Efficiently reject $H_0$ in favor of an alternative $H_1$ | Efficiently reject $H_0$ in favor of an alternative $H_1$ | Efficiently examine the evidence for $H_0$ relative to an alternative $H_1$, or vice versa |
| **Nature of data**  | Cumulative  | Independent  | Cumulative  | Cumulative |
| **Control of error rates** | Direct | Direct | Indirect (e.g., through simulation) |
| **Bias correction procedure**| Available | Does not exist | Available |
| **Flexibility** | Moderately flexible | Highly restrictive | Highly flexible |
| **Acceptance of the null** | Possible | Impossible | Possible |
